A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-07-01 paper/main.tex
revision of regressor correlation fig caption

% t-contrasts
The following three t-contrasts were defined:
1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

\begin{figure*} \centering
\includegraphics[width=\linewidth]{figures/regressor-corr}
\caption{Pearson correlation coefficients of the 26 regressors used in the
    analysis to validate the annotation.
    Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the
    hemodynamic response function and concatenated across runs before
    computing the correlation.}
\label{fig:reg-corr} \end{figure*}

>>>>

% t-contrasts
The following three $t$-contrasts were defined:
1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the 26 regressors used in the analysis to
        validate the annotation. Regressors were created by convolving the
        events with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic
        response function, temporally filtered with the same high-pass filter
        (cut-off \unit[150]{s}) as the BOLD time series, and concatenated across
    runs before computing the correlation.}
    \label{fig:reg-corr}
\end{figure*}
